\documentclass{article}

\usepackage{amsmath}
\usepackage{tikz}
\usepackage{geometry}

% Setting specific margins
\geometry{left=1.5in, top=1in, right=1.5in, bottom=1in}

% Setting paper size
\geometry{a4paper}  % or letterpaper, a5paper, etc.


\title{CHAPTER 0\\
REVIEW OF ALGEBRA\\ 
01. Sets of Real Numbers
}
\author{Exercised by: Rizal Bimanto}
\date{}

\begin{document}
\maketitle
A set is determined by its elements.
Neither rearrangements neither nor repetitions in a listing affects the set.
A $set A$ is said to be a subset of $set B$ if and only if
every element of $A$ is also an element of $B$.\par

For example, if $A = \left\{ 6, 8, 10 \right\}$ and $B = \left\{ 6, 8, 10, 12 \right\}$,
then $A$ is a subset of $B$. However, $B$ is not a subset of $A$.
There is exactly one set which contains no elements.
It is called the empty set and is denoted by Ø.\par

\section{Real Numbers}
Real numbers are a set of numbers which encompass all the possible
numbers that can be represented on a continous number line.
Real numbers may contain various type of numbers. Such as:
\begin{enumerate}

    \item Rational numbers \par 
    These are the numbers that can be expressed as
    \textbf{ratio of two numbers} (where the denominator is not 0).
    \textbf{They can have terminating decimal representations},
    for instances are
    \begin{itemize}
        \item $\frac{3}{4} = 0.75$,
        \item $\frac{1}{5} = 0.4$,
        \item or \underline{non-terminating and repeating decimal numbers}.
        Such as
        \begin{enumerate}
            \item $\frac{1}{3} = 0.33333\dots$,
            \item $- \frac{4}{11} = 0.363636\dots$,
            \item and $\frac{2}{15} = 0.13333\dots$
        \end{enumerate}
    \end{itemize}

    \item Irrational Numbers \par
    These are the numbers that cannot be expressed as a ratio of two integers.
    The decimal expansion are \textbf{non-terminating} and \textbf{non-repeating}.
    Irrational numbers cannot be written as an integer divided by integer.
    Examples:
    \begin{itemize}
        \item $\pi$ (pi)
        \item $e$ (Euler)
        \item $\sqrt{2}$
        \item $\sqrt{3}$
        \item $\sqrt{5}$
        \item $\varphi$ (Golden Ratio)
    \end{itemize}

    \item Integers: \par
    This is a subset of rational numbers that include zero,
    positive whole numbers (natural numbers), and their negatives. \\
    Examples: \dots, -2, -1, 0, 1, 2, \dots

    \item Whole Numbers: \par
    These include all natural numbers along with zero.

    \item Natural Numbers: \par
    Also known as counting numbers. These starts from 1 and go on indefinitely
    (1, 2, 3, \dots) \par
    
    \begin{tikzpicture}
        % Draw the main line
        \draw[thick, ->] (-4,0) -- (4,0) node[right] {Positive direction};
    
        % Manual placement of labels and bullets
        % Integers (label below the line)
        \foreach \x/\xtext in {-3/-3, -2/-2, -1/-1, 0/0, 1/1, 2/2, 3/3} {
            \draw (\x, 0.1) -- (\x, -0.1) node[below] {$\xtext$};
        }
    
        % Non-integers (label above with bullet)
        \foreach \x/\xtext in {-3.14/-\pi, -1.5/-1.5, 0.5/\frac{1}{2}, 1.4142/\sqrt{2}, 3.14/\pi} {
            \filldraw[blue] (\x,0) circle (2pt);
            \node[above] at (\x, 0.2) {$\xtext$};
        }
    
        % Label the origin explicitly if not already done
        \node[align=center, below] at (0, -0.5) {Origin};
    \end{tikzpicture}

\end{enumerate}

\section{Problems}
\textit{
    In problem 1 - 12, determine the truth of each statement.
    If the statement is false, give a reason why is that so.
    }

\begin{enumerate}
    \item $\sqrt{-13}$ is an integer.\par
    \textit{False. It contains decimals} \par

    \item $\frac{-2}{7}$ is rational.\par
    \textit{
        Yes it is rational. Although its decimal is non
        terminating, it's repeating.
    }\par

    \item $-3$ is a positive integer.\par
    \textit{False. It is a negative integer.}\par

    \item $0$ is not rational.\par
    \textit{
        False. It can be a rational. You can put 0
        as a numerator in a fraction.
    }\par

    \item $\sqrt{3}$ is rational.\par
    \textit{
        False. It is irrational. Because it contains non-terminating and
        non-repeating numbers in a decimal form.
    }\par

    \item $\frac{-1}{0}$ is a rational number.\par
    \textit{
        False. It is undefined.
    }\par

    \item $\sqrt{25}$ is not a positive integer.\par
    \textit{
        True. It can be $5$ or $-5$.
    }\par

    \item $\sqrt{2}$ is a real number.\par
    \textit{
        True. It is encompassed in all the possible numbers
        which can be represented in a continous line.
    }\par

    \item $\frac{0}{0}$ is rational.\par
    \textit{
        False. It is undefined.
    }\par

    \item $\pi$ is a positive integer.\par
    \textit{
        False. It is not an integer because it contains decimal.
    }\par

    \item $0$ is to the right of $-\sqrt{2}$ on the real number line.\par
    \textit{
        True.
    }\par

    \item Every integer is positive or negative.\par
    \textit{
        True. Zero, positive whole numbers
        \text{(natural numbers)}, and their negatives.
    }\par

    \item Every terminating decimal number can be regarded as a repeating decimal number.\par
    \textit{
        True. For example is $\frac{1}{2}$ = 0.5000\dots
    }\par

    \item $\sqrt{-1}$ is a real number.\par
    \textit{
        False. Because there is no real numbers squared equals negative number.
    }\par
\end{enumerate}

\end{document}